Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-17 eswc-2012/phdsymp.tex
siste småplukk
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@104 43ef1190-90fd-4dd7-a769-d0121f02b80e

Within the currently published benchmarks, it is up to the user to
select an engine with the best characteristics, relative to their own
expected application. However, I am often asked the question: ``what
is the best general-purpose triple store?'' Those who ask are not
prepared to expand on the question. Thus, we should ask ourselves: 
Can we collapse all the metrics into a single \emph{test
  statistic} that can summarize the performance of the engine as a
whole? Also, can we provide a system for developers that they can use
to see if any changes they do to the engine can have unexpected adverse
effects on other parts of the system? For those who are able to
qualify their inquiry, weighing different parts of the system or
metrics is more useful and will yield a more tenable answer, and
motivates the question: Can we use the system to better find the
distinguishing characteristics so that we can return a question that
will actually help new users of SPARQL engines to chose one that meets
their needs?

The above relies on data and queries that are representative
of the system as a whole. It is often asserted that it is not possible
to create a ``one-size-fits-all'' benchmark (see
e.g. \cite{Schmidt:2011:FBS:2063016.2063054}) to cover all aspects of
an application. While that may be true in the general case, I want to
challenge the assumption that the best we can do is testing queries on
a best effort basis in the case of SPARQL.

>>>>

Within the currently published benchmarks, it is up to the user to
select an engine with the best characteristics, relative to their own
expected application. However, I am often asked the question: ``what
is the best general-purpose triple store?'' Those who ask are usually not
prepared to expand on the question. Thus, we should ask ourselves: 
Can we collapse all the metrics into a single \emph{test
  statistic} that can summarize the performance of the engine as a
whole? Also, can we provide a system for developers that they can use
to see if any changes they do to the engine can have unexpected adverse
effects on other parts of the system? For those who are able to
qualify their inquiry, weighing different parts of the system or
metrics is more useful and will yield a more tenable answer, and
motivates the question: Can we use the system to better find the
distinguishing characteristics so that we can return a question that
will actually help new users of SPARQL engines to chose one that meets
their needs?

The above relies on data and queries that are representative of the
system as a whole. It is often asserted that it is not possible to
create a ``one-size-fits-all'' benchmark (see
e.g. \cite{Schmidt:2011:FBS:2063016.2063054}) to cover all aspects of
an application. While that may be true in the general case, I want to
challenge the assumption that a best effort approach is all we can do
in the case of SPARQL.
